Analysis of bulk void regions

### 2014-04-21 cosmic_voids.tex
Figures and analysis of histogram of volumes for bulk voids, for lambda_th = 0 and lambda_th = optimal.

Following the recent growing interest in studying galaxy formation in 
low-density regions, we use a method based on a FOF-like algorithm to 
find extended regions of voids. To achieve this, we build the input 
catalogue for the FOF method with the coordinate of the center of every 
cell marked as void according to the web classification scheme adopted, 
furthermore we set an adequate linking length to connect even diagonal 
neighbour cells.

Following the work of \SRKED{Forero-Romero et al. 2008}, we also perform a 
percolation analysis in order to select the best threshold parameter that
reduces percolation in cells, thereby accounting for physical bulk void 
regions. In Figure \ref{fig:percolation_analysis} we show the obtained 
result of our percolation analysis for both web schemes. In both cases, it 
can be noticed that the volume of the largest void region is minimized and 
the volume distribution of voids is relatively flat at $\lambda_{th} = 0.0$, 
what means percolation is completely reduced for this threshold value. So, 
in spite of the previously established $\lambda_{th}$ optimal values for 
each scheme, we shall use $\lambda_{th} = 0.0$ just for the detection of 
bulk void regions. Moreover, due to the domination of the large scale 
visual impression by voids, it is inevitable the presence of the 
percolation phenomenon, so the current chosen threshold value for 
percolation is justified because though voids are necessarily connected 
among them, we are just interested in detecting bulk regions.

Next, we shall calculate the reduced inertia tensor of each void region 
in order to determinate their principal directions of inertia and analyse 
the size-shape distribution of voids.

%.........................................................................
%Reduced inertia tensor
\eq{ReducedIntertia}
{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
%.........................................................................
where $l$ is an index associated to each cell of to the current region, 
$i$ and $j$ indexes run over each spatial direction and finally 
$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$, all 
positions are measured from the respective center of mass of the region.

The eigenvalues of the reduced inertia tensor, i.e. the principal moments
of inertia, are used to quantify the shape of void regions. They are 
denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$, where we rather 
calculate histograms for these ratio quantities instead of each single 
value in order to avoid using an arbitrary normalization. For both schemes, 
it can be noticed that the shape-distribution is completely spread out, 
thereby indicating a non-preferred geometry of void regions, which is in 
agreement with the well established highly anisotropy of matter flows
associated to this type of region \SRKED{[reference here]}. Because of 
that, we shall look for possible alignments between the plane of rotation 
of halo pairs and the principal directions of inertia of the nearest void 
regions.

@@

  \captionof{figure}{\small Distribution of masses of dark matter halos
  according the region where they are embedded for both web schemes 
  (upper panels) and of peculiar velocity (lower| panels).}

@@

>>>>

%-------------------------------------------------------------------------
\subsection{FOF void finder}
\label{subsec:fof_finder}
%-------------------------------------------------------------------------

Following the recent growing interest in studying galaxy formation in 
low-density regions as cosmological tests, we propose an scheme to find 
bulk voids by using the two defined web schemes. Initially, we explore a 
first simple method based on a FOF-like algorithm, where we build an input 
catalogue for the FOF method with the coordinate of the center of every 
cell marked as void according to the web classification scheme adopted, 
setting a linking length to connect diagonal neighbour cells.

Following the work of \SRKED{Forero-Romero et al. 2008}, we also perform a
percolation analysis in order to select the best threshold parameter that
reduces percolation in cells. In Figure \ref{fig:percolation_analysis_FOF}
we show the obtained result of our percolation analysis for both web 
schemes. In both cases, it can be noticed that the volume of the largest 
void region is minimized at $\lambda_{th} = 0.0$, what means the 
percolation is completely reduced for this threshold value. However, 
according to our previous analysis, such value does not reproduce the
visual appearance of the cosmic web, so it is out of consideration.

@@

  \captionof{figure}{\small Distribution of masses of dark matter halos
  according the region where they are embedded for both web schemes 
  (upper panels) and of peculiar velocity (lower panels).}

@@

%.........................................................................
%FIGURE 4: Percolation analysis for FOF void finder
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_regions_percolation_FOF.pdf}

  \captionof{figure}{\small Percolation analysis of bulk void found by using
  FOF void finder algorithm. It is swept an extensive \lth range for both web
  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
  volume (lower panel) and the number of bulk voids found (upper panel).}

  \label{fig:percolation_analysis_FOF}
  \vspace{0.1 cm}

%.........................................................................
%FIGURE 5: Percolation analysis for FOF void finder
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}

  \captionof{figure}{\small Percolation analysis of bulk void found by using
  FOF void finder algorithm. It is swept an extensive \lth range for both web
  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
  volume (lower panel) and the number of bulk voids found (upper panel).}

  \label{fig:volume_distributions}
  \vspace{0.1 cm}
